$\pi$ with leftovers: \\ a mechanisation in Agda

### 2020-07-17 paper/paper.tex
Clarify that we use pairs of multiplicities for channels

In the linear \picalc{} each channel has an input and an output \emph{capability}, and each capability has a given \emph{multiplicity} of 0 (exhausted) or 1 (available).
We generalise over this notion by defining an algebra that is satisfied by linear, graded and shared types alike.

>>>>

In the linear \picalc{} each channel has an input and an output \emph{capability}, and each capability has a given \emph{multiplicity} of 0 (exhausted) or 1 (available).
We generalise over this notion of multiplicities by defining an algebra for them that is satisfied by linear, graded and shared types alike.
We then use pairs of multiplicities as usage annotations for channels.
